The Proofs

### 2024-07-31 proofs/tex/ord-lemmas.tex
prettify + minor edits

\lemDistrMuOrd*
\begin{proof}
  Mutual induction on $[[iN]]$ and $[[iP]]$.
  \begin{caseof}
  \item $[[iN]]$ = $[[na]]$ \label{case:distr-mu-ord:var} \\
    let us consider four cases:
    \begin{caseof}
    \item $[[na]] \in A$ and $[[na]] \in [[varset]]$. Then
      \begin{align*} [[ [mu] (ord varset in iN) ]] &= [[ [mu] (ord varset in na)]] \\
                                                             &= [[ [mu] na ]]
                                                             && \text{by \ruleref{\ottdruleOPVarInLabel}}\\
                                                             &= [[nb]]
                                                             && \text{for some $[[nb]] \in B$ (notice $[[nb]] \in [[ [mu]varset ]]$)} \\
                                                             &= [[ ord [mu]varset in nb ]]
                                                             && \text{by \ruleref{\ottdruleOPVarInLabel},
                                                                because $[[nb]] \in [[ [mu]varset ]]$} \\
                                                             &= [[ord [mu] varset in [mu] na ]]
       \end{align*}
     \item $[[na]] \notin A$ and $[[na]] \notin [[varset]]$\\
       Notice that
       $[[ [mu] (ord varset in iN) ]] = [[ [mu] (ord varset in na)]] = [[·]]$ by
       \ruleref{\ottdruleOPVarNInLabel}.
       On the other hand, $[[ ord [mu] varset in [mu] na = ord [mu] varset
       in na ]] = [[·]]$ The latter equality is from
       \ruleref{\ottdruleOPVarNInLabel}, because
       $[[mu]]$ is collision-free on $[[varset]]$ and $[[fv iN]]$, so
       $[[fv iN]] \ni [[na]] \notin [[mu]](A \cap [[varset]]) \cup
       [[varset]] \supseteq [[ [mu] varset ]]$.
     \item $[[na]] \in A$ but $[[na]] \notin [[varset]]$\\ Then
       $[[ [mu] (ord varset in iN) ]] = [[ [mu] (ord varset in na)]] = [[·]]$
       by \ruleref{\ottdruleOPVarNInLabel}.
       To prove that\\ $[[ ord [mu] varset in [mu] na ]] = [[·]]$, we apply
       \ruleref{\ottdruleOPVarNInLabel}. Let us show that
       $[[ [mu] na ]] \notin [[ [mu] varset ]]$.
       Since $[[ [mu] na ]] = [[mu]]([[na]])$ and
       $[[ [mu] varset ]] \subseteq [[mu]](A \cap [[varset]]) \cup [[varset]]$,
       it suffices to prove 
       $[[mu]]([[na]]) \notin [[mu]](A \cap [[varset]]) \cup [[varset]]$.

@@

   \item $[[iN]] = [[iP → iM]]$
     \begin{align*}
        & [[ [mu] (ord varset in iN) ]] \\ 
        &= [[ [mu] (ord varset in iP → iM) ]] \\
        &= [[ [mu] (ordVars1, (ordVars2 \ {ordVars1})) ]]
          && \text{where } [[ord varset in iP = ordVars1]] \text{ and } [[ord varset in iM = ordVars2]] \\
        &= [[ [mu] ordVars1, [mu](ordVars2 \ {ordVars1}) ]] \\
        &= [[ [mu] ordVars1, ([mu]ordVars2 \ [mu]{ordVars1}) ]]
          && \text{by induction on $[[ordVars2]]$;
                  the inductive step is similar to 
                  \cref{case:distr-mu-ord:var}.}\\
        & && \text{Notice that $[[mu]]$ is collision free on $[[{ordVars1}]]$ and $[[{ordVars2}]]$} \\
        & && \text{since
          $[[{ordVars1}]] \subseteq [[varset]]$ and
          $[[{ordVars2}]] \subseteq [[fv iN]]$ }\\
          &= [[ [mu] ordVars1, ([mu]ordVars2 \ {[mu]ordVars1}) ]]
      \end{align*}
      \hfill\\
      On the other hand,
       $[[  ord [mu] varset in [mu]iN ]] = 
        [[ ord [mu] varset in [mu]iP → [mu]iM ]] = 
        [[ ordVarsb1, (ordVarsb2 \ {ordVarsb1}) ]] = 
        [[ [mu] ordVars1, ([mu]ordVars2 \ {[mu]ordVars1}) ]]$,
        where  $[[ord [mu] varset in [mu] iP = ordVarsb1]]$ 
        and $[[ord [mu] varset in [mu] iM = ordVarsb2]]$, 
        then by the induction hypothesis, 
        $[[ordVarsb1]] = [[ [mu] ordVars1 ]]$, 
        $[[ordVarsb2]] = [[ [mu] ordVars2 ]]$.

@@

    \item $[[iN = iP → iM]]$
       \begin{align*}
        [[ ord varset in [σ]iN ]] &= [[ ord varset in [σ](iP → iM) ]] \\
                                   &= [[ ord varset in ([σ]iP → [σ]iM) ]]
                                   && \text{def. of substitution}\\
                                   &= [[ ord varset in [σ]iP]],\\
                                   &\phantom{=} ~ [[(ord varset in [σ]iM \ {ord varset in [σ]iP}) ]]
                                   && \text{def. of ordering}\\
                                   &= [[ ord varset in iP]],\\
                                   &\phantom{=} ~ [[(ord varset in iM \ {ord varset in iP}) ]]
                                   && \text{the induction hypothesis}\\
                                   &= [[ ord varset in iP → iM ]]
                                   && \text{def. of ordering}\\
                                   &= [[ ord varset in iN ]]
       \end{align*}
    \item The proofs of the positive cases are symmetric.
  \end{caseof}
\end{proof}

>>>>

\lemDistrMuOrd*
\begin{proof}
  Mutual induction on $[[iN]]$ and $[[iP]]$.
  \begin{caseof}
  \item $[[iN]]$ = $[[na]]$ \label{case:distr-mu-ord:var} \\
    let us consider four cases:
    \begin{caseof}
    \item $[[na]] \in A$ and $[[na]] \in [[varset]]$. Then
      \begin{align*} [[ [mu] (ord varset in iN) ]] &= [[ [mu] (ord varset in na)]] \\
                                                             &= [[ [mu] na ]]
                                                             && \text{by \ruleref{\ottdruleOPVarInLabel}}\\
                                                             &= [[nb]]
                                                             && \text{for some $[[nb]] \in B$}\\
                                                             & && \text{(notice $[[nb]] \in [[ [mu]varset ]]$)} \\
                                                             &= [[ ord [mu]varset in nb ]]
                                                             && \text{by \ruleref{\ottdruleOPVarInLabel},
                                                                as $[[nb]] \in [[ [mu]varset ]]$} \\
                                                             &= [[ord [mu] varset in [mu] na ]]
       \end{align*}
     \item $[[na]] \notin A$ and $[[na]] \notin [[varset]]$\\
       Notice that
       $[[ [mu] (ord varset in iN) ]] = [[ [mu] (ord varset in na)]] = [[·]]$ by
       \ruleref{\ottdruleOPVarNInLabel}.
       On the other hand, $[[ ord [mu] varset in [mu] na = ord [mu] varset
       in na ]] = [[·]]$ The latter equality is from
       \ruleref{\ottdruleOPVarNInLabel}, because
       $[[mu]]$ is collision-free on $[[varset]]$ and $[[fv iN]]$, so
       $[[fv iN]] \ni [[na]] \notin [[mu]](A \cap [[varset]]) \cup
       [[varset]] \supseteq [[ [mu] varset ]]$.
     \item $[[na]] \in A$ but $[[na]] \notin [[varset]]$\\ Then
       $[[ [mu] (ord varset in iN) ]] = [[ [mu] (ord varset in na)]] = [[·]]$
       by \ruleref{\ottdruleOPVarNInLabel}.
       To prove that\\ $[[ ord [mu] varset in [mu] na ]] = [[·]]$, we apply
       \ruleref{\ottdruleOPVarNInLabel}. Let us show that
       $[[ [mu] na ]] \notin [[ [mu] varset ]]$.
       Since $[[ [mu] na ]] = [[mu]]([[na]])$ and
       $[[ [mu] varset ]] \subseteq [[mu]](A \cap [[varset]]) \cup [[varset]]$,
       it suffices to prove 
       $[[mu]]([[na]]) \notin [[mu]](A \cap [[varset]]) \cup [[varset]]$.

@@

   \item $[[iN]] = [[iP → iM]]$
     \begin{align*}
        & [[ [mu] (ord varset in iN) ]] \\ 
        &= [[ [mu] (ord varset in iP → iM) ]] \\
        &= [[ [mu] (ordVars1, (ordVars2 \ {ordVars1})) ]]
          && \text{where } [[ord varset in iP = ordVars1]] \text{ and } [[ord varset in iM = ordVars2]] \\
        &= [[ [mu] ordVars1, [mu](ordVars2 \ {ordVars1}) ]] \\
        &= [[ [mu] ordVars1, ([mu]ordVars2 \ [mu]{ordVars1}) ]]
          && \text{by induction on $[[ordVars2]]$;
                  the ind. step is similar to 
                  \cref{case:distr-mu-ord:var}.}\\
        & && \text{notice that $[[mu]]$ is collision free on $[[{ordVars1}]]$ and $[[{ordVars2}]]$} \\
        & && \text{since
          $[[{ordVars1}]] \subseteq [[varset]]$ and
          $[[{ordVars2}]] \subseteq [[fv iN]]$ }\\
          &= [[ [mu] ordVars1, ([mu]ordVars2 \ {[mu]ordVars1}) ]]
      \end{align*}
      \hfill\\
      On the other hand,
       $[[  ord [mu] varset in [mu]iN ]] = 
        [[ ord [mu] varset in [mu]iP → [mu]iM ]] = 
        [[ ordVarsb1, (ordVarsb2 \ {ordVarsb1}) ]] = 
        [[ [mu] ordVars1, ([mu]ordVars2 \ {[mu]ordVars1}) ]]$,
        where  $[[ord [mu] varset in [mu] iP = ordVarsb1]]$ 
        and $[[ord [mu] varset in [mu] iM = ordVarsb2]]$, 
        then by the induction hypothesis, 
        $[[ordVarsb1]] = [[ [mu] ordVars1 ]]$, 
        $[[ordVarsb2]] = [[ [mu] ordVars2 ]]$.

@@

    \item $[[iN = iP → iM]]$
       \begin{align*}
        [[ ord varset in [σ]iN ]] &= [[ ord varset in [σ](iP → iM) ]] \\
                                   &= [[ ord varset in ([σ]iP → [σ]iM) ]]
                                   && \text{def. of substitution}\\
                                   &= [[ ord varset in [σ]iP]],\\
                                   &\phantom{=} ~ [[(ord varset in [σ]iM \ {ord varset in [σ]iP}) ]]
                                   && \text{def. of ordering}\\
                                   &= [[ ord varset in iP]],\\
                                   &\phantom{=} ~ [[(ord varset in iM \ {ord varset in iP}) ]]
                                   && \text{the ind. hypothesis}\\
                                   &= [[ ord varset in iP → iM ]]
                                   && \text{def. of ordering}\\
                                   &= [[ ord varset in iN ]]
       \end{align*}
    \item The proofs of the positive cases are symmetric.
  \end{caseof}
\end{proof}

### 2024-07-31 proofs/tex/singularity-lemmas.tex
prettify + minor edits

\lemMinInstSoundness*
\begin{proof}
    We prove it by induction on the inference of $[[Γ ⊢ uP SC minby uσ ]]$.
    Let us consider the last rule used in the inference.
    \begin{caseof}
        \item \ruleref{\ottdruleSINGPUvarLabel}, which means 
            that the inferred judgment is $[[Γ ⊢  α̂⁺ SC minby (nf(iP) / α̂⁺)]]$, 
            and by inversion, $[[(α̂⁺ :≥ iP) ∊ SC]]$. Let us show the required properties:
            \begin{itemize}
                \item $[[Θ ⊢ (nf(iP) / α̂⁺) : uv α̂⁺]]$ holds trivially;
                \item $[[Θ ⊢  (nf(iP) / α̂⁺) : SC]]$ holds since
                    $[[Γ ⊢ nf(iP) : (α̂⁺ :≥ iP)]]$, which is true 
                    since $[[Γ ⊢ nf(iP) ≥ iP]]$ by the soundness of normalization
                    (\cref{lemma:normalization-soundness});
                \item $[[(nf(iP) / α̂⁺)]]$ is normalized trivially;
                \item let us take an arbitrary $[[Θ ⊢ uσ' : {α̂⁺} ]]$
                    respecting $[[SC]]$. Since $[[uσ']]$ respects $[[SC]]$,
                    $[[Γ ⊢ [uσ']α̂⁺ ≥ iP]]$ holds, and then
                    $[[Γ ⊢ [uσ']α̂⁺ ≥ nf(iP)]]$ holds by the soundness of normalization
                    and transitivity of subtyping. Finally,
                    $[[Γ ⊢ [uσ']α̂⁺ ≥ nf(iP)]]$ can be rewritten as
                    $[[Γ ⊢ [uσ']α̂⁺ ≥ [(nf(iP) / α̂⁺)]α̂⁺]]$.
            \end{itemize}
        \item \ruleref{\ottdruleSINGExistsLabel}, which means that 
            the inferred judgment has form $[[Γ ⊢ ∃nas.uP SC minby uσ ]]$,
            and by inversion, $[[Γ, nas ⊢ uP SC minby uσ]]$.
            By applying the induction hypothesis to $[[Γ, nas ⊢ uP SC minby uσ]]$
            we have 
            \begin{itemize}
                \item $[[Θ ⊢ uσ : uv uP]]$, which also means $[[Θ ⊢ uσ : uv ∃nas.uP]]$,
                \item $[[Θ ⊢ uσ : SC]]$,
                \item $[[uσ]]$ is normalized, and
                \item for any other $[[Θ ⊢ uσ' : uv uP ]]$
                    respecting $[[SC]]$ (\ie $[[Θ ⊢ uσ' : SC]]$), we have
                    $[[Γ, nas ⊢ [uσ']uP ≥ [uσ]uP ]]$, which immediately implies 
                    $[[Γ ⊢ [uσ']∃nas.uP ≥ [uσ]∃nas.uP ]]$ (the left-hand side
                    existential variables are instantiated with the corresponding 
                    right-hand side existential variables).
            \end{itemize}
        \item \ruleref{\ottdruleSINGSingLabel}, which means that
            the inferred judgment has form $[[Γ ⊢ uP SC minby uσ]]$,
            and by inversion, $[[uv(uP) ⊆ dom(SC)]]$ and
            $[[SC|uv(uP) singular with uσ]]$. Let us apply the soundness of singularity
            (\cref{lemma:singularity-soundness}) to $[[SC|uv(uP) singular with uσ]]$ to
            obtain the following properties:
            \begin{itemize}
                \item $[[ Θ ⊢ uσ : uv(uP) ∩ dom(SC) ]]$, which also means 
                    $[[Θ ⊢ uσ : uv(uP)]]$,
                \item $[[Θ ⊢ uσ : SC|uv(uP)]]$,
                \item $[[uσ]]$ is normalized, and
                \item for any other $[[Θ ⊢ uσ' : uv(uP) ]]$
                    respecting $[[SC|uv(uP)]]$, we have
                    $[[Θ ⊢ uσ' ≈ uσ : uv(uP)]]$. The latter means that
                    $[[Γ ⊢ [uσ']uP ≈ [uσ]uP]]$, and in particular, 
                    $[[Γ ⊢ [uσ']uP ≥ [uσ]uP]]$.
            \end{itemize}
    \end{caseof}

@@

            If the entry restricting $[[α̂⁺]]$ in $[[SC]]$ is an \emph{equivalence} entry
            ($[[(α̂⁺ :≈ iQ) ∊ SC]]$), then we wish to apply
            \ruleref{\ottdruleSINGSingLabel}.
            The first premise $[[uv(α̂⁺) ⊆ dom(SC)]]$  
            holds by assumption;
            to infer $[[SC|{α̂⁺} singular with uσ0]]$, 
            we apply the completeness of singularity (\cref{lemma:singularity-completeness}).
            It applies because all the substitutions satisfying $[[SC|{α̂⁺}]] = [[(α̂⁺ :≈ iQ)]]$
            are equivalent on $[[{α̂⁺}]]$ by transitivity of equivalence 
            (\cref{corollary:equivalence-transitivity}): 
            the satisfaction of this constraint means that the substitution 
            sends $[[α̂⁺]]$ to $[[iQ]]$ or an equivalent type.
            This way, $[[SC|{α̂⁺} singular with uσ0]]$ for some $[[uσ0]]$,
            which means $[[Γ ⊢ α̂⁺ SC minby uσ0]]$.
            To show that $[[uσ0 = nf(uσ)]]$ notice that 
            Since $[[uσ0]]$ is normalized and equivalent to $[[uσ]]$ on $[[{α̂⁺}]]$, 
            and only has $[[α̂⁺]]$ in its domain
            (by soundness of singularity, \cref{lemma:singularity-soundness}).
            This way, $[[Γ ⊢ α̂⁺ SC minby uσ]]$, as required.
        \item  \label{case:min-inst-completeness-down}
            $[[uP = ↓uN]]$. Then since
            $[[Γ ⊢ ↓[uσ']uN ≥ ↓[uσ]uN ]]$ means
            $[[Γ ⊢ ↓[uσ']uN ≈ ↓[uσ]uN ]]$ by inversion.
            Then by \cref{lemma:subst-equiv}, 
            $[[uσ]]$ is equivalent to any other substitution 
            $[[Θ ⊢ uσ' : uv uN ]]$ satisfying $[[SC|uv uN]]$,
            hence, the completeness of singularity (\cref{lemma:singularity-completeness})
            can be applied to conclude that
            \begin{itemize}
                \item $[[uv(uN) = dom(SC|uv uN)]]$, then $[[uv(uP) ⊆ dom(SC)]]$,
                \item $[[SC|uv uN singular with uσ0]]$ for some (normalized) $[[uσ0]]$.
            \end{itemize}
            It means $[[Γ ⊢ uP SC minby uσ0 ]]$, and then
            since $[[uσ0]]$ is normalized and equivalent to $[[uσ0]]$ on $[[uv(uN)]]$,
            and its domain is $[[uv(uN)]]$, $[[uσ0 = nf(uσ)]]$.
        % \item $[[uP = ∃nas.uP']]$ 
        %     Then we wish to apply the induction hypothesis to show 
        %     $[[Γ, nas ⊢ uP' SC minby nf(uσ)]]$, which would imply 
        %     $[[Γ ⊢ ∃nas.uP' SC minby nf(uσ)]]$ by \ruleref{\ottdruleMINExistsLabel}.
        %     Let us demonstrate that the premises of the induction hypothesis hold. 
        %     \begin{itemize}
        %         \item  $[[Γ, nas ⊢ Θ]]$ holds by weakening;
        %         \item  $[[Γ, nas; dom(Θ) ⊢ uP']]$ holds by inversion of $[[Γ; dom(Θ) ⊢ uP]]$;
        %         \item $[[uv uP' = uv uP]]$, and 
        %                 $[[Γ ⊢ [uσ']∃nas.uP' ≥ [uσ]∃nas.uP' ]]$ implies
        %                 $[[Γ, nas ⊢ [uσ']uP' ≥ [uσ]uP' ]]$ by \cref{lemma:subst-equiv}.
        %     \end{itemize}

        \item $[[uP = ∃nas.β⁺]]$ then 
            as there are no algorithmic variables in $[[uP]]$, 
            $[[nf([uσ]uP) = β⁺]]$,
            and thus, we wish to show that 
            $[[Γ ⊢ ∃nas.β⁺ SC minby ·]]$.
            To do so, we apply \ruleref{\ottdruleSINGExistsLabel},
            and it is left to show that $[[Γ, nas ⊢ β⁺ SC minby · ]]$,
            which holds vacuously by \ruleref{\ottdruleSINGSingLabel}.
        \item $[[uP = ∃nas.α̂⁺]]$ then 
            $[[Γ ⊢ [uσ']∃nas.α̂⁺ ≥ [uσ]∃nas.α̂⁺ ]]$ implies 
            $[[Γ ⊢ ∃nas.[uσ']α̂⁺ ≥ ∃nas.[uσ]α̂⁺ ]]$ implies 
            $[[Γ ⊢ [uσ']α̂⁺ ≥ [uσ]α̂⁺ ]]$.
            It means that $[[uσ]]$ instantiates $[[α̂⁺]]$ to the minimal 
            type among all the instantiations of $[[α̂⁺]]$ respecting $[[SC]]$.
            In other words, we can apply the reasoning from 
            \cref{case:min-inst-completeness-uvar}
            to conclude that $[[Γ ⊢ α̂⁺ SC minby nf(uσ) ]]$.
            And then \ruleref{\ottdruleSINGExistsLabel}
            gives us $[[Γ ⊢ ∃nas.α̂⁺ SC minby nf(uσ) ]]$.
        \item $[[uP = ∃nas.↓uN]]$ then 
            $[[Γ ⊢ [uσ']∃nas.↓uN ≥ ∃nas.↓[uσ]uN ]]$ implies 
            $[[Γ ⊢ ∃nas.↓[uσ']uN ≥ ∃nas.↓[uσ]uN ]]$ implies
            $[[Γ, nas ⊢ ↓[σ0][uσ']uN ≥ ↓[uσ]uN ]]$ for some $[[σ0]]$ implies
            $[[Γ, nas ⊢ [σ0][uσ']uN ≈ [uσ]uN ]]$.
            By \cref{lemma:subst-equiv}, it means in particular
            that $[[uσ']]$ and $[[uσ]]$ are equivalent on 
            $[[uv uN]]$. 
            This way, we can apply the completeness of singularity 
            (\cref{lemma:singularity-completeness}), and continue as in
            \cref{case:min-inst-completeness-down}
            to conclude that $[[Γ, nas ⊢ ↓uN SC minby nf(uσ)]]$.
            Then by \ruleref{\ottdruleSINGExistsLabel},
            we have $[[Γ ⊢ ∃nas.↓uN minby nf(uσ)]]$.
    \end{caseof}
\end{proof}

>>>>

\lemMinInstSoundness*
\begin{proof}
    We prove it by induction on the inference of $[[Γ ⊢ uP SC minby uσ ]]$.
    Let us consider the last rule used in the inference.
    \begin{caseof}
        \item \ruleref{\ottdruleSINGPUvarLabel}, which means 
            that the inferred judgment is $[[Γ ⊢  α̂⁺ SC minby (nf(iP) / α̂⁺)]]$, 
            and by inversion, $[[(α̂⁺ :≥ iP) ∊ SC]]$. Let us show the required properties:
            \begin{itemize}
                \item $[[Θ ⊢ (nf(iP) / α̂⁺) : uv α̂⁺]]$ holds trivially;
                \item $[[Θ ⊢  (nf(iP) / α̂⁺) : SC]]$ holds since
                    $[[Γ ⊢ nf(iP) : (α̂⁺ :≥ iP)]]$, which is true 
                    since $[[Γ ⊢ nf(iP) ≥ iP]]$ by the soundness of normalization
                    (\cref{lemma:normalization-soundness});
                \item $[[(nf(iP) / α̂⁺)]]$ is normalized trivially;
                \item let us take an arbitrary $[[Θ ⊢ uσ' : {α̂⁺} ]]$
                    respecting $[[SC]]$. Since $[[uσ']]$ respects $[[SC]]$,
                    $[[Γ ⊢ [uσ']α̂⁺ ≥ iP]]$ holds, and then
                    $[[Γ ⊢ [uσ']α̂⁺ ≥ nf(iP)]]$ holds by the soundness of normalization
                    and transitivity of subtyping. Finally,
                    $[[Γ ⊢ [uσ']α̂⁺ ≥ nf(iP)]]$ can be rewritten as
                    $[[Γ ⊢ [uσ']α̂⁺ ≥ [(nf(iP) / α̂⁺)]α̂⁺]]$.
            \end{itemize}
        \item \ruleref{\ottdruleSINGExistsLabel}, which means that 
            the inferred judgment has form $[[Γ ⊢ ∃nas.uP SC minby uσ ]]$,
            and by inversion, $[[Γ, nas ⊢ uP SC minby uσ]]$.
            By applying the induction hypothesis to $[[Γ, nas ⊢ uP SC minby uσ]]$
            we have 
            \begin{itemize}
                \item $[[Θ ⊢ uσ : uv uP]]$, which also means $[[Θ ⊢ uσ : uv ∃nas.uP]]$,
                \item $[[Θ ⊢ uσ : SC]]$,
                \item $[[uσ]]$ is normalized, and
                \item for any other $[[Θ ⊢ uσ' : uv uP ]]$
                    respecting $[[SC]]$ (\ie $[[Θ ⊢ uσ' : SC]]$), we have
                    $[[Γ, nas ⊢ [uσ']uP ≥ [uσ]uP ]]$, which immediately implies 
                    $[[Γ ⊢ [uσ']∃nas.uP ≥ [uσ]∃nas.uP ]]$ (the left-hand side
                    existential variables are instantiated with the corresponding 
                    right-hand side existential variables).
            \end{itemize}
        \item \ruleref{\ottdruleSINGSingLabel}, which means that
            the inferred judgment has form $[[Γ ⊢ uP SC minby uσ]]$,
            and by inversion, $[[uv uP ⊆ dom(SC)]]$ and
            $[[SC|uv uP singular with uσ]]$. Let us apply the soundness of singularity
            (\cref{lemma:singularity-soundness}) to $[[SC|uv uP singular with uσ]]$ to
            obtain the following properties:
            \begin{itemize}
                \item $[[ Θ ⊢ uσ : uv uP ∩ dom(SC) ]]$, which also means 
                    $[[Θ ⊢ uσ : uv uP]]$,
                \item $[[Θ ⊢ uσ : SC|uv uP]]$,
                \item $[[uσ]]$ is normalized, and
                \item for any other $[[Θ ⊢ uσ' : uv uP ]]$
                    respecting $[[SC|uv uP]]$, we have
                    $[[Θ ⊢ uσ' ≈ uσ : uv uP]]$. The latter means that
                    $[[Γ ⊢ [uσ']uP ≈ [uσ]uP]]$, and in particular, 
                    $[[Γ ⊢ [uσ']uP ≥ [uσ]uP]]$.
            \end{itemize}
    \end{caseof}

@@

            If the entry restricting $[[α̂⁺]]$ in $[[SC]]$ is an \emph{equivalence} entry
            ($[[(α̂⁺ :≈ iQ) ∊ SC]]$), then we wish to apply
            \ruleref{\ottdruleSINGSingLabel}.
            The first premise $[[uv α̂⁺ ⊆ dom(SC)]]$  
            holds by assumption;
            to infer $[[SC|{α̂⁺} singular with uσ0]]$, 
            we apply the completeness of singularity (\cref{lemma:singularity-completeness}).
            It applies because all the substitutions satisfying $[[SC|{α̂⁺}]] = [[(α̂⁺ :≈ iQ)]]$
            are equivalent on $[[{α̂⁺}]]$ by transitivity of equivalence 
            (\cref{corollary:equivalence-transitivity}): 
            the satisfaction of this constraint means that the substitution 
            sends $[[α̂⁺]]$ to $[[iQ]]$ or an equivalent type.
            This way, $[[SC|{α̂⁺} singular with uσ0]]$ for some $[[uσ0]]$,
            which means $[[Γ ⊢ α̂⁺ SC minby uσ0]]$.
            To show that $[[uσ0 = nf(uσ)]]$ notice that 
            Since $[[uσ0]]$ is normalized and equivalent to $[[uσ]]$ on $[[{α̂⁺}]]$, 
            and only has $[[α̂⁺]]$ in its domain
            (by soundness of singularity, \cref{lemma:singularity-soundness}).
            This way, $[[Γ ⊢ α̂⁺ SC minby uσ]]$, as required.
        \item  \label{case:min-inst-completeness-down}
            $[[uP = ↓uN]]$. Then since
            $[[Γ ⊢ ↓[uσ']uN ≥ ↓[uσ]uN ]]$ means
            $[[Γ ⊢ ↓[uσ']uN ≈ ↓[uσ]uN ]]$ by inversion.
            Then by \cref{lemma:subst-equiv}, 
            $[[uσ]]$ is equivalent to any other substitution 
            $[[Θ ⊢ uσ' : uv uN ]]$ satisfying $[[SC|uv uN]]$,
            hence, the completeness of singularity (\cref{lemma:singularity-completeness})
            can be applied to conclude that
            \begin{itemize}
                \item $[[uv uN = dom(SC|uv uN)]]$, then $[[uv uP ⊆ dom(SC)]]$,
                \item $[[SC|uv uN singular with uσ0]]$ for some (normalized) $[[uσ0]]$.
            \end{itemize}
            It means $[[Γ ⊢ uP SC minby uσ0 ]]$, and then
            since $[[uσ0]]$ is normalized and equivalent to $[[uσ0]]$ on $[[uv uN]]$,
            and its domain is $[[uv uN]]$, $[[uσ0 = nf(uσ)]]$.
        % \item $[[uP = ∃nas.uP']]$ 
        %     Then we wish to apply the induction hypothesis to show 
        %     $[[Γ, nas ⊢ uP' SC minby nf(uσ)]]$, which would imply 
        %     $[[Γ ⊢ ∃nas.uP' SC minby nf(uσ)]]$ by \ruleref{\ottdruleMINExistsLabel}.
        %     Let us demonstrate that the premises of the induction hypothesis hold. 
        %     \begin{itemize}
        %         \item  $[[Γ, nas ⊢ Θ]]$ holds by weakening;
        %         \item  $[[Γ, nas; dom(Θ) ⊢ uP']]$ holds by inversion of $[[Γ; dom(Θ) ⊢ uP]]$;
        %         \item $[[uv uP' = uv uP]]$, and 
        %                 $[[Γ ⊢ [uσ']∃nas.uP' ≥ [uσ]∃nas.uP' ]]$ implies
        %                 $[[Γ, nas ⊢ [uσ']uP' ≥ [uσ]uP' ]]$ by \cref{lemma:subst-equiv}.
        %     \end{itemize}

        \item $[[uP = ∃nas.β⁺]]$ then 
            as there are no algorithmic variables in $[[uP]]$, 
            $[[nf([uσ]uP) = β⁺]]$,
            and thus, we wish to show that 
            $[[Γ ⊢ ∃nas.β⁺ SC minby ·]]$.
            To do so, we apply \ruleref{\ottdruleSINGExistsLabel},
            and it is left to show that $[[Γ, nas ⊢ β⁺ SC minby · ]]$,
            which holds vacuously by \ruleref{\ottdruleSINGSingLabel}.
        \item $[[uP = ∃nas.α̂⁺]]$ then 
            $[[Γ ⊢ [uσ']∃nas.α̂⁺ ≥ [uσ]∃nas.α̂⁺ ]]$ implies 
            $[[Γ ⊢ ∃nas.[uσ']α̂⁺ ≥ ∃nas.[uσ]α̂⁺ ]]$ implies 
            $[[Γ ⊢ [uσ']α̂⁺ ≥ [uσ]α̂⁺ ]]$.
            It means that $[[uσ]]$ instantiates $[[α̂⁺]]$ to the minimal 
            type among all the instantiations of $[[α̂⁺]]$ respecting $[[SC]]$.
            In other words, we can apply the reasoning from 
            \cref{case:min-inst-completeness-uvar}
            to conclude that $[[Γ ⊢ α̂⁺ SC minby nf(uσ) ]]$.
            And then \ruleref{\ottdruleSINGExistsLabel}
            gives us $[[Γ ⊢ ∃nas.α̂⁺ SC minby nf(uσ) ]]$.
        \item $[[uP = ∃nas.↓uN]]$ then 
            $[[Γ ⊢ [uσ']∃nas.↓uN ≥ ∃nas.↓[uσ]uN ]]$ implies 
            $[[Γ ⊢ ∃nas.↓[uσ']uN ≥ ∃nas.↓[uσ]uN ]]$ implies
            $[[Γ, nas ⊢ ↓[σ0][uσ']uN ≥ ↓[uσ]uN ]]$ for some $[[σ0]]$ implies
            $[[Γ, nas ⊢ [σ0][uσ']uN ≈ [uσ]uN ]]$.
            By \cref{lemma:subst-equiv}, it means in particular
            that $[[uσ']]$ and $[[uσ]]$ are equivalent on 
            $[[uv uN]]$. 
            This way, we can apply the completeness of singularity 
            (\cref{lemma:singularity-completeness}), and continue as in
            \cref{case:min-inst-completeness-down}
            to conclude that $[[Γ, nas ⊢ ↓uN SC minby nf(uσ)]]$.
            Then by \ruleref{\ottdruleSINGExistsLabel},
            we have $[[Γ ⊢ ∃nas.↓uN SC minby nf(uσ)]]$.
    \end{caseof}
\end{proof}
